Turkey Hemorrhagic Enteritis Virus transcription profiling

### 2023-03-17 README.Rmd
Update Project README.Rmd

![project_map](./project_map.svg){width=720px height=620px}

@@

```{r include = FALSE}

script_dir <- for(item in list.files("scripts")){
    print(item, quote = FALSE)}

rawfiles_dir <- for(item in list.files("raw_files")){
    print(item, quote = FALSE)}

results_dir <- for(item in list.files("results")){
    print(item, quote = FALSE)
}
```
* **`ROOT (thev_transcriptome)`**
    * **Directories:**
        * *`scripts`*
        * *`raw_files`*
        * *`results`*
        * *`trimmedReads`*
    * **Files**
        * *`Snakefile`*
        * *`driver_script`* - *`deprecated`*
        * *`README.Rmd`*
        * *`project_map.pdf`* 
        * *`project_jobmap.pdf`*
        * *`thev_transcriptome.Rproj`* - *not on Git*
    * **Hidden files**
        * `.gitignore`
        * `.Rproj.user` - *not tracked*
        * `.snakemake` - *not tracked*

@@

- `Hisat-2`
- `StringTie`
- `R`
- `Snakemake`
- `zsh shell`

>>>>

![project_map](./project_map.svg){width=620px height=480px}

@@

```{r list_dirs, exclude=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
dirs <- list.dirs(".", recursive = F, full.names = F)
all_files <- list.files(".", all.files = T)
root_files <- subset(all_files, all_files %in% dirs == FALSE)
script_dir <- list.files("scripts")
rawfiles_dir <- list.files("raw_files")
results_dir <- list.files("results")
reads_dir <- list.files("trimmedReads")

```
* **`ROOT (thev_transcriptome)/`**
    * **Directories:**
        * *``r dirs[4]`/`* - Add README for more details
            * ``r rawfiles_dir[1]`/`
            * ``r rawfiles_dir[2]`/`
            * ``r rawfiles_dir[3]`/`
        * *``r dirs[5]`/`* - Add README for more details
            * ``r results_dir[1]`/`
            * ``r results_dir[2]`/`
            * ``r results_dir[3]`/`
        * *``r dirs[6]`/`* - Add README for more details
            * ``r script_dir[1]`/`
            * ``r script_dir[2]`/`
            * ``r script_dir[3]`/`
        * *``r dirs[7]`/`* - Add README for more details
            * ``r reads_dir[1]`/`
            * ``r reads_dir[2]`/`
    * **Files**
        * *``r root_files[5]``* - *`deprecated`*: replaced by `Snakefile`
        * *``r root_files[6]``*
        * *``r root_files[7]``*
        * *``r root_files[8]``*
        * *``r root_files[9]``*
        * *``r root_files[10]``*
        * *``r root_files[11]``*
        * *``r root_files[12]``*
        * *``r root_files[13]``* - *not on Git*
    * **Hidden files** - *not on Git*
        * *``r root_files[3]``*
        * *``r root_files[4]``*
        * ``r dirs[1]`/`
        * ``r dirs[2]`/`
        * ``r dirs[3]`/`

`r script_dir`

@@

- `Hisat-2`
- `StringTie`
- `R`
- `Snakemake`
- `zsh shell`
- See `environment.yml` for `conda env` dependencies
